Model-View-Controller Package

### 2006-01-26 inst/doc/MVCClass.Rnw
Added a new version of paper 2.  Must have also made a few small changes to the code.
git-svn-id: file:///home/git/hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MVCClass@15900 bc3139a8-67e5-0310-9ffc-ced21a209358

When creating a plot of a data set, there is a general class, called
\Robject{plotView}, that has the slots, plotDevice, plotPar, and drArea, which
store the device number of the plot, the plotting parameters, and the Gtk
drawing area object, respectively.  This class is not intended to have any
objects as it just represents a general plot.  The plot classes that can have
objects are the specific plot classes, \Robject{sPlotView},
\Robject{graphView}, and \Robject{heatmapView}, which inherit from the
\Robject{plotView} class.

@@

Currently, there are two types of messages for messaging within a model, view,
controller object: an add and an update message.  Both the add message,
\Robject{gAddMessage}, and the update message, \Robject{gUpdateMessage},
contain three slots, dataName, mData, and type.  dataName is the character
string that gives the name of the model, mData is a list of data needed to
perform the addition or alteration operation, and type is a character string
that gives the type of addition or alteration to perform.  Although
\Robject{gAddMessage} and \Robject{gUpdateMessage} are not virtual classes, it
is not intended to create objects of these classes.

>>>>

When creating a plot of a data set, there is a general class, called
\Robject{plotView}, that has the slots, plotDevice, plotPar, and drArea, which
store the device number of the plot, the plotting parameters, and the Gtk
drawing area object, respectively.  This class is a virtual class because it
is not intended to have any objects as it just represents a general plot.  The
plot classes that can have
objects are the specific plot classes, \Robject{sPlotView},
\Robject{graphView}, and \Robject{heatmapView}, which inherit from the
\Robject{plotView} class.

@@

Currently, there are two types of messages for messaging within a model, view,
controller object: an add and an update message.  Both the add message,
\Robject{gAddMessage}, and the update message, \Robject{gUpdateMessage},
contain three slots, dataName, mData, and type.  dataName is the character
string that gives the name of the model, mData is a list of data needed to
perform the addition or alteration operation, and type is a character string
that gives the type of addition or alteration to perform.  Both
\Robject{gAddMessage} and \Robject{gUpdateMessage} are virtual classes.
